Neural Circuit Discovery

### 2013-11-05 docs/paper/paper.tex
Konrad's comments ont ext

The rise of connectomics data allows discovery of cell types
based on connectivity information.

@@

We apply it to the recently-released mouse retina connectome, the
c. elegans connectome, and a ``connectome'' obtained by
reverse-engineering a portion of a classical microprocessor.

@@

\section{Results}

\subsubsection{Mouse Retina}
When applied to the mouse retina dataset, we recover spatially-homogeneous patterns of activity that reflect a coarsening of ground truth.

\subsection{C. elegans}
When applied to c. elegans, we segregate ``head and sensor'' interneurons from the spatially-distributed neurons along the body axis.

\subsection{Microprocessor}

\section{Discussion}

>>>>

The advent of connectomics data allows discovery of cell types based
on connectivity information. The rise of clustering had a substantial
impoact on molecular biology, and is now the only way that molecular
biologists are able to deal with high-throughput sequencing
technologies.

[bAyesian nonparametric techniques have been proposed to 
discover structure in data, which could be applied to connecomics data]

@@

We apply it to three very-different computing systems:
recently-released mouse retina connectome, the c. elegans connectome,
and a ``connectome'' obtained by reverse-engineering a portion of a
classical microprocessor.

In all cases, we recover known types and suggest possible new types.

\section{Results}
[add paragraph that summarizes methods and the question]

\subsubsection{Mouse Retina}
intro paragraph about retina data

When applied to the mouse retina dataset, we recover
spatially-homogeneous patterns of activity by anlayzing the
connectivity data.

This recovers structure similar to that known by neuroanatomists [ground truth]

\subsection{C. elegans}
intro paragraph to c elegans data

When applied to c. elegans, we segregate ``head and sensor'' interneurons from the spatially-distributed neurons along the body axis.

\subsection{Microprocessor}
intro paragraph to microprocessor data

\section{Discussion}
We present a machine learning technique that allows cell types to be
disocvered using only connectivity data.

[Two parts: First is how you suck -- cover the things that are missing
such as adding additional features ]

[second is : how this changes things]

In the future, we plan to extend our model with the ability to handle
other classes of information, including genetic and histochemical
metadata.

@@
